A pipeline to analyse time-course gene expression data

### 2019-08-13 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\begin{itemize}
\tightlist
\item
  Why \texttt{dependicies=FALSE}? (same for the README for the repos). Seems easier to just say dependencies=TRUE and avoid the install.R routine.
\item
  I got an error in installation script for packages:
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \texttt{biocLite} is no longer the recommended way to install bioconductor. Instead
  \texttt{BiocManager::install(c("edge",\ "NMI"))}. But this is dependent on
  bioconductor/R version. Also, now that docker, can you change the
  installation to just be simple one-liner (and \texttt{BiocManager::install} can
  also do non-bioc packages, and is much more reliable.)
\end{itemize}

@@

\textbf{EAP: It would be nice to be able to subset in \texttt{plot\_splines\_data/plot\_splines\_data} to only some of the groups}

>>>>

\begin{itemize}
\tightlist
\item
  I got an error in installation script for packages:
\end{itemize}

@@

@@
